---
title: "transportation model"
author: "Nikhil Reddy Addula"
date: "2022-10-19"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(lpSolveAPI)
library(lpSolve)
library(tinytex)
library(ggplot2)
```

```{r}
price <- matrix(c(22,14,30,600,100,16,20,24,625,120,80,60,70,"-","-"), ncol=5,byrow=TRUE)

colnames(price) <- c("Warehouse1","Warehouse2","Warehouse3","ProductionCost", "ProductionCapacity")

rownames(price) <- c("Plant1","Plant2","Demand")

price <- as.table(price)
price
```
$$Minimize\ the\ transportation\ cost\ is\ the\ objective\ function.$$
X = 622Y11 + 614Y12 + 630Y13 + 0Y14 + 641Y21 + 645Y22 + 649Y23 + 0Y24

$$Subject\ to\ the\ following\ constraints$$

Supply Constraints

Y11 + Y12 + Y13 + Y14 <= 100

Y21 + Y22 + Y23 + Y24 <= 120

Demand Constraints

Y11 + Y21 >= 80

Y12 + Y22 >= 60

Y13 + Y23 >= 70

Y14 + Y24 >= 10

Non − Negativity Constraints

Yij >= 0 Where i = 1,2 and j = 1,2,3,4

```{r}
#cost matrix for given objective function

trans_price = matrix(c(622,614,630,0,641,645,649,0),ncol = 4,byrow = T)
trans_price
```
```{r}
#define column name and row names
colnames(trans_price)<-c("warehouse1","warehouse2","warehouse3","Dummy")

rownames(trans_price)<-c("plant1","plant2")

trans_price
```

```{r}
#setting up constrains
plan.signs<- rep("<=",2)
plant.capacity<-c(100,120)
warehouse.signs<-rep(">=",4)
month.demand<-c(80,60,70,10)
```

```{r}
#lp.transport function
lptrans.price<- lp.transport(trans_price,"min", plan.signs,plant.capacity,warehouse.signs,month.demand)
```

```{r}
#getting the objective value
lptrans.price$objval
```

```{r}
#getting the constraints value
lptrans.price$solution
```

80 AEDs in Plant 2 - Warehouse1

60 AEDs in Plant 1 - Warehouse2

40 AEDs in Plant 1 - Warehouse3

30 AEDs in Plant 2 - Warehouse3 To reduce the total cost of manufacturing and transportation, should be created in each plant and then delivered to each of the three wholesaler warehouses.

$$Create\ the\ dual\ of\ the\ above\ transportation\ issue.$$
Since the primary goal was to reduce transportation costs, the secondary goal would be to increase value added (VA).

Maximize VA = 100P1 + 120P2 − 80W1 − 60W2 − 70W3

Subject to the following constraints

Total Profit Constraints

N1 − R1 >= 622

N2 − R1 >= 614

N3 − R1 >= 630

N1 − R2 >= 641

N2 − R2 >= 645

N3 − R2 >= 649

Where N1 = Warehouse 1

N2 = Warehouse 2

N3 = Warehouse 3

R1 = Plant 1

R2 = Plant 2

Economic Interpretation of the dual

N1 >= R1 + 622

N2 >= R1 + 614

N3 >= R1 + 630

N1 >= R2 + 641

N2 >= R2 + 645

N3 >= R2 + 649

The restrictions listed above, which are based on the economic interpretation of the dual, adhere to the maximizing of profits principle, which states that MR >= MC. where MC stands for marginal cost and MR for marginal cost.

$$ Warehouse1 >= Plant1 + 621\ i.e. MR1 >= MC1$$

The difference between marginal cost (MC), or the income produced for each extra unit sold, and marginal revenue, or The income earned for each extra unit sent to Warehouse 1 should exceed or be equivalent to the change in cost at Plant 1 caused by increasing the supply function.

Businesses can utilize this to balance their production output with expenses in order to increase profits.