---
title: "Integer  Programming"
author: "Nikhil Reddy Addula"
date: "2022-11-20"
output:
  word_document: default
  html_document:
    df_print: paged
---

AP is a shipping service that guarantees overnight delivery of packages in the continental US. 
The company has various hubs at major cities and airports across the country. Packages are 
received at hubs, and then shipped to intermediate hubs or to their final destination. 
 
The manager of the AP hub in Cleveland is concerned about labor costs, and is interested in 
determining the most effective way to schedule workers. The hub operates seven days a week, 
and the number of packages it handles varies from one day to another. The table below provides 
an estimate of the number of workers needed each day of the week. 

```{r}
#Loading lpSolveAPI package
library(lpSolveAPI)
getwd()
#setting working directory
setwd("/Users/nikhilreddya")
#loading the lp file
My_table <- read.lp("My_table.lp")
My_table
```
```{r}
#The number of employees required on each day of the week is estimated in the table below.
Workers_Required <-matrix(c("Sunday","Monday","Tuesday","Wednesday","Thursday","Friday","Saturday",
18,27,22,26,25,21,19),ncol=2,byrow = F)
colnames(Workers_Required) <- c("Day_of_the_week", "Workers_Required")
as.table(Workers_Required)

```

Package handlers at AP are guaranteed a five-day work week with two consecutive days off. The 
base wage for the handlers is $750 per week. Workers working on Saturday or Sunday receive an 
additional $25 per day. The possible shifts and salaries for package handlers are: 

```{r}
DayOffs_wages_emp <- matrix(c(1,2,3,4,5,6,7,
                               "Sunday and Monday","Monday and Tuesday","Tuesday and Wednesday",
"Wednesday and Thursday","Thursday and Friday","Friday and Saturday","Saturday and Sunday",
                               "$775","$800","$800","$800","$800","$775","$750"),ncol=3,byrow=F)
colnames(DayOffs_wages_emp) <- c("Shift", "Days_Off", "Wage")
as.table(DayOffs_wages_emp)
```

```{r}
solve(My_table)
```
```{r}
get.objective(My_table)

```
Total cost = $25675
```{r}
get.variables(My_table)
```

The variables are labeled from x1, x2.......x7 where,

*x1 = Number of workers assigned to shift 1 = 2

*x2 = Number of workers assigned to shift 2 = 4

*x3 = Number of workers assigned to shift 3 = 5

*x4 = Number of workers assigned to shift 4 = 0

*x5 = Number of workers assigned to shift 5 = 8

*x6 = Number of workers assigned to shift 6 = 1

*x7 = Number of workers assigned to shift 7 = 13

Hence, the workers availabe for each day is 
```{r}
Available <- matrix(c(0,4,5,0,8,1,0,0,0,5,0,8,1,13,2,0,0,0,8,1,13,2,4,0,0,8,1,13,2,4,5,0,0,1,13,2,3,4,0,0,0,13,2,4,5,0,8,0,0), ncol=7,byrow=TRUE)
colnames(Available)<- c("Shift1", "Shift2", "Shift3", "Shift4", "Shift5", "Shift6", "Shift7")
row.names(Available) <- c('Sunday', 'Monday', 'Tuesday','Wednesda','Thursday','Friday','Saturday')
Available

rowSums(Available)
```